The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-03-11 paper/paper.Rmd
Switched image png -> pdf

```{r scbi-simulation, out.width="100%", fig.cap="Root mean squared error of models for standard, permuted, and spatial cross-validated error estimates. The dotted lines show non-permuted competitor identity, while the histogras so the RMSE for 49 permutations. The colors indicate whether cross validaton was used.", echo = FALSE}
include_graphics("simulation_results/2021-03-03_scbi_49_shuffles.png")
```

>>>>

```{r scbi-simulation, out.width="100%", fig.cap="Comparison of root mean squared error of models for standard, permuted, and spatial cross-validated error estimates. The dotted lines show non-permuted competitor identity, while the histogras so the RMSE for 49 permutations. The colors indicate whether cross validaton was used.", echo = FALSE}
include_graphics("simulation_results/2021-03-03_scbi_49_shuffles.pdf")
```
